### 2018-05-10 General WLD combinatorics.tex
Combined section 2.1 and 2.2 into a more coherent stream

%*****************
%Other useful mathematical operations and functions
\newcommand{\D}{\partial}
\newcommand{\rk}{\textrm{rk }}
\newcommand{\spn}{\textrm{span }}
\newcommand{\rd}{\textrm{d}}
\newcommand{\Res}{\textrm{Res}}
%*****************

@@

\begin{dfn} \label{VPropdfn}
Let $W = (\cP, n)$.
\begin{enumerate}
\item For $p \in \cP$, let $V_p = \{i_p, i_p+1, j_r, j_r+1\}$\note{This has a notational problem, should $p$ be the subscript or $r$.  I think $p$ is better and is entirely clear, but strictly speaking that's not what Definition~\ref{WLdfn} says (though in this case since we don't know the index of $p$ we don't have any way to write $p$'s ends by a strict interpretation of Definition~\ref{WLdfn}).} be the set of vertices supporting $p$. Then, for $P \subset \cP$, the set $V_P = \cup_{p \in P} V_p$ is the vertex support of $P$.\note{I don't like using $\subset$ in a mixed audience because whether or not $\subset$ is strict depends on whether you are an algebraic geometer (and some other related areas) or not so in a mixed audience it is unclear.}
\item For $V \subset [n]$, write $\Prop(V) = \{ p \in \cP | V_p \cap V \neq \emptyset \} $.
\end{enumerate}
\end{dfn}

@@

\begin{dfn}\label{equivdfn}\note{Maybe it would be clearer to say the equivalence relation generated by $W$ and $W'$ which satisfy $1$ and $2$; this helps the note in the next example be less awkward too.}
There is an equivalence relationship on the set of admissible Wilson loops diagrams: $W = (\cP, n)$ and $W'= (\cP', n)$ are equivalent if
\begin{enumerate}
\item There exist two different exact subdiagrams, $(P, V(P))$ and $(P', V(P'))$ of $W$ and $W'$ respectively such that $V(P) =  V(P')$.
\item The complementary subdiagrams are identical: $(\cP \setminus P, V(P)^c) = (\cP' \setminus P', V(P')^c)$.
\end{enumerate}
\end{dfn}

@@

The diagrams $W_1 \equiv W_2$ because $(\{(5,8), (5,7), \{5,6,7,8,1\})$ and $(\{(5,8), (7,8), \{5,6,7,8,1\})$ are the corresponding differing subdiagrams. Furthermore, there is the equivalence $W_2 \equiv W_3$ due to the exact subdiagrams $(\{(1,4), (3,4)\}, \{1,2,3,4,5\})$ and $(\{(1,4), (1,3)\}, \{1,2,3,4,5\})$. This forces an equivalence between $W_1$ and $W_3$, even though one cannot partition the propagators of each into a an exact subdiagram (that may vary between the diagrams) and a complement that is fixed.  \end{eg}

@@

Next, we show that this is the only condition under which two Wilson loop diagrams define the same matroid.

\begin{thm}
Two Wilson loop diagrams define the same matroid if and only if the are equivalent.
\end{thm}

@@

\begin{dfn} For a Wilson Loop diagram $W = (\cP, [n])$, the associated matroid $M(W)$ can be defined by any of the following sets of subsets
\begin{enumerate}
\item A basis of $W$ is any independent set, $B \subset [n]$ of size $|B| = |\cP|$.
\item The rank of a set $|V| \subset [n]$, is bounded above by $\rk(V) \leq \min\{ |V| , |\Prop(V)|\}$. If $V$ is an independent set, then $\rk(V) = |V|$\note{The spacing is weird in $\rk$.  Looking at your definition I think it is on purpose, so I think I'm missing something as to why.  It looks particularly odd when there is a subscript to the rank eg after Def 2.10}. Furthermore, if $v \in [n]$, and $q \in \Prop(v)$, then for any $V \subset [n]$ such that $q \not \in \Prop(V)$, $\rk(V \cup v) = \rk(V) +1$. That is, adding a vertex that supports a new propagator to a set increases the rank of the set.
\item A circuit of a matroid is any set $C \subset [n]$ such that every proper subset $U \subsetneq C$ is independent. That is, $\rk(C) = |C|-1$. The union of circuits is called a cycle. If $C$ is a circuit of an admissible Wilson loop diagram, and $e \in C$, \bas |\Prop(C\setminus e))| \leq |C\setminus e| = \rk(C) \leq \min\{|C|, |\Prop(C\setminus e)|\}\;.\eas
    In other words, if $C$ is a circuit of a Wilson loop diagram, then \bas \rk(C) = |C|-1 = |\Prop(C)| \;. \eas
\item A flat, $F$, of a matroid is a maximally dependent set \note{Maximal for its rank is better than maximally dependent.  Alternately maybe maximal for dependence would be better, but in that case I would really just be meaning rank again}. That is, for all $e \not \in F$ $\rk(F \cup e) = \rk(F) +1$. If $W$ is an admissible Wilson loop diagram, any group of propagators defines a flat, $F(P) = V(P^c)^c$, called a propagator flat. It consists of all vertices of $W$ that do not support any propagators outside of $P \subset \cP$. To see that this is flat, let $v \in V(P^c)$. We have that there is a $q \not \in P$ such that $q \in \Prop(v)$. Therefore, by the rank function, $\rk( F(P) \cup v))> \rk(F(P))$.
\end{enumerate}
\end{dfn}

Furthermore, in \cite{wilsonloops}, the authors show that if $F$ is a cyclic flat, then there is a $P \subset \cP$ such that $F = F(P)$.

@@

\begin{cor} \label{classifyflats}
If $F$ is a flat of a Wilson loop diagram, it can be written as the union of a cyclic flat, and thus a propagator flat, and an independent flat.\note{What would you think of putting ``and thus a propagator flat'' in parentheses or something; otherwise I'm concerned that the nesting structure of this sentence is not sufficiently clear.}
\end{cor}
From this we see that any propagator flat can be written as a union of a cyclic propagator flat and an independent flat.

@@

In the sequel, I conflate a Wilson loop diagram with the matroid it defines.

\subsection{Exact subdiagrams and matroids}

It has been proved that if two Wilson loop diagrams are equivalent, then the define the same matroid in ``Matroids and Wilson Loop Diagrams''. In this section, we prove the converse. Therefore, we prove several results about exact subdiagrams.

@@

In what follows, maximal exact subdiagrams play a significant role. First, we show that maximal exact subdiagrams of an admissible Wilson loop diagram are disjoint.

\begin{lem}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $(Q, V(Q))$, $(R, V(R))$ two maximal exact subdiagrams. Then $Q\cap R = \emptyset$.
\end{lem}

@@

@@

While one still cannot equate a subdiagram with a restriction, this lemma allows one to write a maximal exact subdiagram as a contraction. First, recall a result from \cite{wilsonloops} about contracted diagrams and matroids.

\begin{lem}
For $W = (\cP, [n])$, write the contracted diagram $W/P = (P^c, V(P)^c)$. If $\rk F(P) = |P|$, we may identify \bas M(W/P) = M(W)/ F(P) \;. \eas
\end{lem}

In other words, a maximally exact subdiagram $(P, V(P))$  can be written as a contraction by the complementary propagator flat: \bas (P, V(P)) = W/F(P^c) \;.\eas

@@

\begin{thm}
Let $W= (\cP, [n])$ and $W'= (\cP', [n])$ be two Wilson Loop diagrams. They define the same matroid if and only if $W \sim W'$.
\end{thm}
\note{I don't understand how this section (and this theorem) relate to the preivous section, which has the same content in its main theorem.}

@@

Reorganize the vertex sets as follows: \ba \cup_{P_i \neq P_i'} V(P_i) = V(\cup_{P_i \neq P'_i} P_i)  \label{vertexsets}\; .\ea Since maximal exact subdiagrams are disjoint, and single propapagators may define maximal subdiagrams, $\cup_{i = 1}^k P_i = \cup_{i = 1}^k P'_i = \cP$. Then equation \eqref{vertexsets} becomes \bas \cap_{P_i \neq P_i'} (F(P_i^c))^c = F(\cup_{P_j = P'_j} P_j)^c \;.\eas These flats may, of course, be empty.\todo{Is this paragraph necessary?}

@@

\subsection{Counting exact subdiagrams}

Since equivalent Wislon loop diagrams are the only ones that define the same matroid as each other, it is useful to enumerate the number of equivalent diagrams any Wilson loop diagram has.

\begin{dfn}
  Let $W$ be an admissible Wilson loop diagram.  The \emph{polygon partition} associated to $W$, denotes $\tau(W)$ is defined as follows.
  \begin{itemize}
  \item The vertices of $\tau(W)$ correspond to the edges of $W$.
  \item The polygon of $\tau(W)$ is the graph theoretic cycle made of the vertices of $\tau(W)$ and where two vertices are adjacent if the corresponding edges of $W$ meet at a vertex of $W$.
  \item There is a chord edge of $\tau(W)$ for each propagator of $W$.  Given a propagator fo $W$, this edge of $\tau(W)$ joins the two vertices of $\tau(W)$ corresponding to the edges of $W$ where the two ends of the propagator lie.
  \end{itemize}
\end{dfn}

For an admissible $W$ no propagators cross and so no chord edges of $\tau(W)$ cross.  Thus, in graph theoretic language, we can view $\tau(W)$ as a planar embedding of a graph with no cut vertices, where all vertices lie on the infinite face, along with a distinguished start vertex and direction around the infinite face.  From this viewpoint the polygon of $tau(W)$ is the boundary of the infinite face.

\begin{dfn}
  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition.
  A \emph{triangulated piece} of $\tau(W)$ is a 2-connected subgraph of $\tau(W)$ which is a triangulation and which is maximal with respect to that property.  We will take the convention that a subgraph consisting of two vertices joined by an edge which is in no triangle is also a triangulated piece, called a \emph{trivial} triangulated piece.
\end{dfn}

\begin{lem}
  Every polygon partition $\tau(W)$ has a unique decomposition into triangulated pieces.
\end{lem}

\begin{proof}
  First consider the weaker notion of decompositions of $\tau(W)$ into 2-connected pieces which are either triangulations (but not necessarily maximal) or subgraphs consisting of two vertices joined at an edge.  At least one such decomposition must exist as we can simply take each edge as defining it's own subgraph.

  Now suppose we have two distinct such decompositions.  Since they are distinct there must be some edge $e$ of $\tau(W)$ for which the subgraph containing this edge are differs between the decompositions.  Let $T_1$ and $T_2$ be these two subgraphs.  The graph $T_1\cup T_2$ defined by taking the union of the vertex sets of $T_1$ and $T_2$ along with the union of the edge sets of $T_1$ and $T_2$ is still a subgraph of $\tau(W)$.  Furthermore, since all vertices of $\tau(W)$ lie on the external face, and $T_1$ and $T_2$ are 2-connected, then $T_1$ and $T_2$ can share at most two vertices and these must be on the external faces of $T_1$ and of $T_2$.  Therefore $T_1\cup T_2$ is the result of gluing two triangulations along edges on each of their external faces and hence is also a triangulation.  Combining all subgraphs which share edges we obtain a decomposition containing both original decompositions.

  Therefore the set of such decompositions of $\tau(W)$ is not just a poset under containment but is a finite directed set and thus has a unique maximal element.

Also, the subgraphs making up this maximal element are themselves maximal as if not then taking the union with the decomposition formed from a single triangulation which properly contains one of the triangulations of the maximal element along with the remaining edges as individual subgraphs, would give a decompositions containing the purported maximal one.  Furthermore, no non-maximal decomposition can be a decomposition into maximal triangulations because since it is properly contained in the maximal element some subgraph of this decomposition must be properly contained in some subgraph of the maximal decomposisiton and hence not be a maximal triangulation.

  Thus the maximal decomposition is the desired unique decomposition into (maximal by definition) triangulated pieces.
\end{proof}

That previous proof is rather belaboured, so it will probably want to be cut down, but I'm not sure which parts will be obvious to our audience and which will not be.

\begin{lem}\label{lem triang to exact}
  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition.  The nontrivial triangulated pieces of $\tau(W)$ correspond to the maximal connected exact subdiagrams of $W$.
\end{lem}

  Since $W$ is admissible, $\tau(W)$ has no double edges and so is a simple graph.
  Let $t$ be a nontrivial triangulated piece of $\tau(W)$ and suppose $t$ has $n$ vertices.  We want to count how many edges of $t$ are not on the outer face of $\tau(W)$.  Consider the intersection of $t$ with the outer face of $\tau(W)$.  This is a subgraph with $n$ vertices of the polygon of $\tau(W)$, call it $S$.  Let $k$ be the number of connected components of $S$.  Also $S$ is a spanning subgraph of the outer face of $t$ and $S$ has $n$ edges.  To join the components $S$ must have $k$ edges not in the outer face of $\tau(W)$.  Furthermore $t$ has $n-3$ edges not in its outer face and so also not in the outer face of $\tau(W)$.  Thus there are $n-3+k$ edges of $t$ not in the outer face of $\tau(W)$.

  These edges correspond to propagators in $W$, so the open subdiagram of $W$ corresponding to $\tau(W)$ has $n-3+k$ propagators.  Next let's count the vertices of this subdiagram.  Each of the $n$ vertices in the outer face of $t$ corresponds to an edge of the open subdiagram and the edges of this open subdiagram form $k$ connected compnents of the outer polygon.  Thus the open subdiagram has $n+k$ vertices.  So we see that the open subdiagram corresponding to $t$ has exactly three more vertices than propagators.  Propagators can never be supported at higher density than this by admissibility and so the support of the propagators of the subdiagram is all the vertices of the subdiagram and hence the subdiagram is exact.  We have not used the maximality of the triangulation in the above and so any triangulated subgraph corresponds to an exact subdiagram.

  Conversely if we have an exact subdiagram of $W$ with $n$ edges forming $k$ connected components of the outer polygon then the corresponding subgraph of $\tau(W)$ has $n$ vertices and $n-k+(n-3+k) = 2n-3$ edges, of which $n$ are in the outer face and hence is a triangulation.

  The statement of the lemma then follows form the fact that inclusion is preserved under $\tau$ and so maximality also corresponds under $\tau$.
\end{proof}

@@

>>>>

%*****************
%Other useful mathematical operations and functions
\newcommand{\D}{\partial}
\newcommand{\rk}{\textrm{rk}}
\newcommand{\spn}{\textrm{span }}
\newcommand{\rd}{\textrm{d}}
\newcommand{\Res}{\textrm{Res}}
%*****************

@@

\begin{dfn} \label{VPropdfn}
Let $W = (\cP, n)$.
\begin{enumerate}
\item For $p \in \cP$, let $V_p = \{i_p, i_p+1, j_p, j_p+1\}$ be the set of vertices supporting $p$. Then, for $P \subseteq \cP$, the set $V_P = \cup_{p \in P} V_p$ is the vertex support of $P$.
\item For $V \subseteq [n]$, write $\Prop(V) = \{ p \in \cP | V_p \cap V \neq \emptyset \} $.
\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be the set of vertices in $[n]$ that only support propagators in the set $P$. 
\end{enumerate}
\end{dfn}

It is sometimes useful to discuss propagators in terms of the edges supporting them, rather than the vertices.

\begin{dfn}
The $i^{th}$ edge of $W$ is the edge of the external polygon that lies between the vertices $i$ and $i+1$. 
\end{dfn}

In this manner, the propagator $p = (i, j)$ is supported by the $i^{th}$ and $j^{th}$ edges.

@@

\begin{dfn}\label{equivdfn}
There is an equivalence relationship on the set of admissible Wilson loops diagrams generated by the following binary relation: $W = (\cP, n) \sim W'= (\cP', n)$ if
\begin{enumerate}
\item There exist two different exact subdiagrams, $(P, V(P))$ and $(P', V(P'))$ of $W$ and $W'$ respectively such that $V(P) =  V(P')$.
\item The complementary subdiagrams are identical: $(\cP \setminus P, V(P)^c) = (\cP' \setminus P', V(P')^c)$.
\end{enumerate}
\end{dfn}

@@

The diagrams $W_1 \sim W_2$ because $(\{(5,8), (5,7), \{5,6,7,8,1\})$ and $(\{(5,8), (7,8), \{5,6,7,8,1\})$ are the corresponding differing subdiagrams. Furthermore, there is the equivalence $W_2 \sim W_3$ due to the exact subdiagrams $(\{(1,4), (3,4)\}, \{1,2,3,4,5\})$ and $(\{(1,4), (1,3)\}, \{1,2,3,4,5\})$. This forces an equivalence between $W_1$ and $W_3$, even though one cannot partition the propagators of each into a an exact subdiagram (that may vary between the diagrams) and a complement that is fixed.  \end{eg} \note{Did you change $\sim$ to $\equiv$? Or was I being flaky? If you prefer different notation, lets discuss.}

@@

In the remainder of this section, we show that two admissible Wilson loop diagrams define the same matroid if an only if they are equivalent. Furthermore, we count the number of Wilson loop diagrams in each equivalence class. The first of these are done by considering Wilson loop diagrams as matroids. The second, by considering polygon partitions of Wilson Loop Diagrams.

@@

\begin{dfn} For a Wilson Loop diagram $W = (\cP, [n])$, the associated matroid $M(W)$ can be defined by any of the following sets of subsets
\begin{enumerate}
\item An set $V \subseteq [n]$ is independent if there is no subset that supports fewer propagators than vertices of that subset: \bas \not \exists U \subseteq V \; \textrm{s.t. } |\Prop (U)| < |U|\;. \eas A basis of $W$ is any independent set, $B \subset [n]$ of size $|B| = |\cP|$.
\item The rank of a set $|V| \subset [n]$, is bounded above by $\rk(V) \leq \min\{ |V| , |\Prop(V)|\}$. If $V$ is an independent set, then $\rk(V) = |V|$. Furthermore, if $v \in [n]$, and $q \in \Prop(v)$, then for any $V \subset [n]$ such that $q \not \in \Prop(V)$, $\rk(V \cup v) = \rk(V) +1$. That is, adding a vertex that supports a new propagator to a set increases the rank of the set.
\item A circuit of a matroid is any set $C \subset [n]$ such that every proper subset $U \subsetneq C$ is independent. That is, $\rk(C) = |C|-1$. The union of circuits is called a cycle. If $C$ is a circuit of an admissible Wilson loop diagram, and $e \in C$, \bas |\Prop(C\setminus e))| \leq |C\setminus e| = \rk(C) \leq \min\{|C|, |\Prop(C\setminus e)|\}\;.\eas
    In other words, if $C$ is a circuit of a Wilson loop diagram, then \bas \rk(C) = |C|-1 = |\Prop(C)| \;. \eas
\item A flat, $F$, of a matroid is a set that is maximal for its rank. That is, for all $e \not \in F$ $\rk(F \cup e) = \rk(F) +1$. If $W$ is an admissible Wilson loop diagram, any group of propagators defines a flat, $F(P) = V(P^c)^c$, called a propagator flat. To see that this is flat, let $v \in V(P^c)$. We have that there is a $q \not \in P$ such that $q \in \Prop(v)$. Therefore, by the rank function, $\rk( F(P) \cup v))> \rk(F(P))$. Furthermore, in \cite{wilsonloops}, the authors show that if $F$ is a cyclic flat, then there is a $P \subset \cP$ such that $F = F(P)$.

\end{enumerate}
\end{dfn}

@@

\begin{cor} \label{classifyflats}
If $F$ is a flat of a Wilson loop diagram, it can be written as the union of a cyclic propagato flat and an independent flat. \end{cor}

In particular, any propagator flat can be written as a union of a cyclic propagator flat and an independent flat.

Finally, we note the differences between subdiagrams of Wilson loop diagrams, and restrictions or contractions of the associated matroids.

@@

A subdiagram is more closely related to a contracted matroid.

\begin{lem} \label{contractsubdiaglem}
For $W = (\cP, [n])$, consider a subdiagram $(P^c, V(P^c))$. The complementary set of vertices is a propagator flat: $F(P) = V(P^c)^c$. If this has maximal rank, $\rk F(P) = |P|$, then the subdiagram defines the same matroid as is formed by contracting the original matroid by $F(P)$: \bas M((P^c, V(P^c))) = M(W)/ F(P) \;. \eas
\end{lem}

In the sequel, where it doesn't cause confusion, I conflate a Wilson loop diagram with the matroid it defines.

\subsection{Polygon partitions of Wilson loop diagrams}

In order to study exact Wilson loop diagrams, we further introduce the notion of a polygon partition of $W$.

\begin{dfn}
  Let $W = (\cP, n)$ be an admissible Wilson loop diagram.  The \emph{polygon partition} associated to $W$, denotes $\tau(W)$ is defined as follows.
  \begin{itemize}
  \item The vertices of $\tau(W)$ correspond to the edges of $W$. 
  \item Labeling the edges of $\tau(W)$ with the edge number gives a cyclic order to the vertices. Connecting consecutive vertices gives a graph theoretic cycle called the polygon of $\tau(W)$.
  \item Each propagator of $W$ defines a chord edge of $\tau(W)$ for each propagator of $W$.  If $p= (i,j) \in \cP$, it defines a chord connecting the verices $i$ and $j$
  \end{itemize}
\end{dfn}

\begin{lem}\label{tausimpleplanarlem}
If $W = (\cP, n)$ is an admissible Wilson loop diagram, $\tau(W)$ is a simple planar graph with cyclically ordered vertices. It is embedded such that the vertices all like on the infinite face.
\end{lem}

\begin{proof}
Since the vertices of $\tau(W)$ are labeled by the edges of $W$, which are cyclically ordered, this gives an ordering to the vertices. Since $W$ is admissible, no pairs of propagators cross. Thereofore, it is a planar embedding. There are no propagators $p = (i, i+1)$. Therefore, there is exactly one edge connecting any two adjacent edges of $\tau(W)$. Similarly, there are not two propagators such that both $p$ and $q$ start and end at the edges $i$ and $j$. Therefore, no other two vertices of $\tau(W)$ can be connected by more than one edge. Finally, the embedding of $\tau(W)$ is induced from embedding of the graph $W$. 
 \end{proof}

\hlfix{For an admissible $W$ no propagators cross and so no chord edges of $\tau(W)$ cross.  Thus, in graph theoretic language, we can view $\tau(W)$ as a planar embedding of a
graph with no cut vertices, where all vertices lie on the infinite face, along with a distinguished start vertex and direction around the infinite face.  From this viewpoint the polygon of $tau(W)$ is the boundary of the infinite face.}{I've smushed this together a bit in the prev. lem. Tell me if I've missed anything. Its a lemma for emphasis, not difficulty}

\begin{dfn}
  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition. A \emph{triangulated piece} of $\tau(W)$ is a 2-connected subgraph of $\tau(W)$ which is a triangulation. We will take the convention that a subgraph consisting of {\color{red}two non-adjascent} vertices joined by an edge  is also a triangulated piece, called a \emph{trivial} triangulated piece.
\end{dfn}

\begin{lem} \label{decompositionlem}
  For $W$ an admissible Wilson loop diagram, the polygon partition $\tau(W)$ has a unique decomposition into maximal triangulated pieces, and boundary edges. 
\end{lem}

\begin{proof}
We begin by giving an algorithm for the decomposition, then prove its uniqueness.

Let $T(W)$ be a the dual graph of $\tau(W)$ with the vertex corresponding the to the infinite face removed. In other words, place a vertex on each finite face of $\tau(W)$. These vertices are connected if there is a chord edge separating the edges. Furthermore, if the face is bounded by an edge of the polygonal cycle of $\tau(W)$, the corresponding vertex gets a leaf edge for each such boundary. Since, by Lemma \ref{tausimpleplanarlem}, $\tau(W)$ is a simple planar graph, this \hlfix{$T(W)$ is an uniquely defined tree.}{Why do I know it is a tree? }

By construction, each face of $\tau(W)$ is a polygon. Therefore, each vertex of $T(W)$ is at least 3 valent (one for each edge of the polygon). If split each vertex of $T(W)$ if it is strictly greater than $3$ valent. (In other words, we fail to split exactly when the face is a triangle). The connected components of $T(W)$ correspond to the decomposition of $\tau(W)$ into maximal triangulated pieces. The the vertices of the forest thus obtained have valence 1, corresponding to root or leaf vertices, or 3, corresponding to triangulated faces. Subtrees with no trivalent vertices correspond to either edges of the boundary of $\tau(W)$, if they were originally leaves of $T(W)$, or to maximal trivial triangulations. \hlfix{Splitting at all the faces that are not triangles ensures maximality of the decomposition.}{more words?}

\hlfix{To see uniqueness, consider the uniqueness of $T(W)$. If there were two different decompositions of $\tau(W)$, this would imply that there are two different ways to split a vertex of $T(W)$, which implies the n0n-uniqueness of the valency of the vertices of $T(W)$, which contradicts the uniqueness of $T(W)$.}{Your proof was much more complicated. What am I missing?}
\end{proof}

\subsection{Exact subdiagrams}

It has been proved that if two Wilson loop diagrams are equivalent, then the define the same matroid in \cite{wilsonloops}. In this section, we prove that two Wilson loop diagrams are equivalent if and only if they define the same matroid. Furthermore, we count the admissible elements of each equivalence class.

We begin by relating triangulations and exact subdiagrams.

\begin{lem}\label{lem triang to exact}
  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition.  The triangulated pieces of $\tau(W)$ correspond to the exact subdiagrams of $W$.
\end{lem}

  Since $W$ is admissible, by lemma \ref{} $\tau(W)$ is a simple graph. Furthermore, $t$ is not all of $\tau(W)$.
  Let $t$ be a triangulated piece of the decomposition of $\tau(W)$ given in Lemma \ref{decomplem} and suppose $t$ has $n>2$ vertices.  We want to count how many edges of $t$ are not on the outer face of $\tau(W)$.  Consider the intersection of $t$ with the outer face of $\tau(W)$.  This is a possibly disconnected subgraph of the polygon of $\tau(W)$ with $n$ vertices, call it $S$.  Let $k$ be the number of connected components of $S$. \hlfix{Also $S$ is a spanning subgraph of the outer face of $t$ and $S$ has $n$ edges.}{Not sure what this means. There are 4 edges in the picture you sent.}  To join the components $S$ must have $k$ edges not in the outer face of $\tau(W)$.  Furthermore $t$ has $n-3$ edges not in its outer face and so also not in the outer face of $\tau(W)$.  Thus there are $n-3+k$ edges of $t$ not in the outer face of $\tau(W)$.

  Each of these $n-3-k$ internal edges correspond to propagators in $W$, call this set $P$.  Next we count the size of $V(P)$.  Each of the $n$ vertices in the outer face of $t$ corresponds to an edge of $W$. These $n$ edges define $k$ connected compnents of the outer polygon of $W$. Thus the set$V(P)$ has $n+k$ vertices.  In other words, \bas |V(P)| = n+k = |P| -3\;.\eas

If $n=2$, then $t$ has two connected componenents. Therefore, $t$ corresponds to a propagator that connects two non-adjacent edges. Therefore, the trivial triangulation is a trivial exact subdiagram.

  Conversely if we have an exact subdiagram $(P, V(P))$ of $W = (\cP, n)$ supported on $|V(P)| = |P|+3$ vertices. Let $|P| = k>1$ and $k+3 = m$. Suppose the set $V(P)$ defines $c$ disjoint cyclic intervals of $[n]$. Then the corresponding subgraph of $\tau(W)$ has $m-c$ vertices. Call it $t$. If $t$ were a triangulated component, $t$ would have $k -c$ internal edges.

  The graph $t$ has $k$ edges that come from propagators, and $m - 2c$ edges that come from the boundary polygon of $\tau(W)$. Since $t$ has $m-c$ vertices, it has $m-c$ external edges, of which $c$ come from propagators. Therefore, of the $k$ edges of $t$ that come from propagators, $k-c$ are internal to the connected component. Therefore, this is triangulated.

  If $k=1$, and $(P, V(P))$ is a trivially exact subdiagram. Then $t$ is an edge internal to $\tau(W)$ connecting two boundary edges, which, by definition is a triangulation.

%  The statement of the lemma then follows form the fact that inclusion is preserved under $\tau$ and so maximality also corresponds under $\tau$.
\end{proof}

Next, we prove a few theorems about matroidal properties of exact subdiagrams.

@@

Therefore, in keeping with Lemma \ref{lem triang to exact}, maximal exact subdiagrams of $W$ correspond to maximal triangular components of $\tau(W)$. In what follows, maximal exact subdiagrams/ maximal triangulations play a significant role. First, we show that maximal exact subdiagrams of an admissible Wilson loop diagram are disjoint.

\begin{cor}
For $W = (\cP, n)$ can be uniquely decomposed into maximal exact subdiagrams.
\end{cor}

\begin{proof}
This is a corollary to Lemma \ref{decompositionlem}, that gives a unique decomposition of polygon partitions, $\tau(W)$,  into maximal triangulated pieces, and Lemma \ref{lem triang to exact}, which gives a correspondence between triangulated components and exact subdiagrams.
\end{proof}

Furthermore, we can show that maximal triangulated pieces are disjoint in $\tau(W)$. \note{do we have this already?}

\begin{lem} \label{disjointexactsubdiagslem}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $(Q, V(Q))$, $(R, V(R))$ two maximal exact subdiagrams. Then $Q\cap R = \emptyset$.
\end{lem}

@@

Finally, we discuss some flats formed by the complement of the propagators defining an exact subdiagram.

@@

In other words, by Lemma \ref{contractsubdiaglem}a maximally exact subdiagram $(P, V(P))$  can be written as a contraction by the complementary propagator flat: \bas (P, V(P)) = W/F(P^c) \;.\eas

@@

\begin{thm}
Let $W= (\cP, [n])$ and $W'= (\cP', [n])$ be two Wilson Loop diagrams. They define the same matroid if and only if $W \sim W'$.
\end{thm}

@@

Reorganize the vertex sets as follows: \ba \cup_{P_i \neq P_i'} V(P_i) = V(\cup_{P_i \neq P'_i} P_i)  \label{vertexsets}\; .\ea Since maximal exact subdiagrams are disjoint, and single propapagators may define maximal subdiagrams, $\cup_{i = 1}^k P_i = \cup_{i = 1}^k P'_i = \cP$. Then equation \eqref{vertexsets} becomes \bas \cap_{P_i \neq P_i'} (F(P_i^c))^c = F(\cup_{P_j = P'_j} P_j)^c \;.\eas These flats may, of course, be empty.

Thus, we have partitioned the vertices of $W$ and $W'$ into a single set that supports a union of maximal exact subdiagrams whose propagators between $W$ and $W'$, and the complementary propagator flats that support the propagators in common between $W$ and $W'$. As mentioned above, the latter may be empty.

@@

\begin{comment}
\subsection{Counting exact subdiagrams}

@@

\end{comment}
